---
title: "extra point"
output: 
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    #pdf_document
date: "2022-11-29"
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelsummary)
library(ggplot2)
```

# In this presentation, we are going to look at 3 practical tools to make data visualization more effective.


### 1. Special coloring options of plots
```{r echo=FALSE, message=FALSE, warning=FALSE}
# create dataframe for demo 
age <- c(11:60)
weight <- c(40,41,45,48,45,44,50,45,55,48,floor(runif(30, min=40, max=60)),60,61,60,58,56,58,55,50,48,45)
height <- c(150,153,157,160,161,167,170,170,172,175, floor(runif(30, min=170, max=175)),170, 167,165,164,163,161,160,160,159,158)

df <- data.frame(age, weight, height)

demo <- ggplot(df) +
  geom_point(aes(x = weight, y = height, color = age), size = 3)+
  theme_classic()+
  #scale_color_gradient(low = "orange", high = "blue")
scale_color_viridis_c()

demo

```

### 2. Adjusting Legends' color and shape of plots

```{r echo=FALSE, message=FALSE, warning=FALSE}
# create dataframe for demo2
name <- sample(c("Mary", "Paul", "Chris"), size=50, replace=TRUE)
weight <- c(40,41,45,48,45,44,50,45,55,48,floor(runif(30, min=40, max=60)),60,61,60,58,56,58,55,50,48,45)
height <- c(150,153,157,160,161,167,170,170,172,175, floor(runif(30, min=170, max=175)),170, 167,165,164,163,161,160,160,159,158)

df2 <- data.frame(name, weight, height)

# add/change colors, shapes and legend titles
colors <- c("Mary" = "red", "Paul" = "navyblue", "Chris" = "darkgreen")
shape <- c("Mary" = 1, "Paul" = 2, "Chris" = 0)

demo2 <- ggplot(df2, aes(weight, height)) +
  geom_point(aes(shape = name, colour = name), size = 3) +
  theme_classic() #+
  #scale_colour_manual(values = colors) #+
  #scale_shape_manual(values = shape) #+
theme(legend.position = "top")

demo2
```


### 3. Positioning & Sizing of plots

changing its position
```{r, fig.align="center"}
# {r, fig.align="center"}
demo

```

changing its size without effect on the ratio (smaller)
```{r dpi=50}
# {r dpi=50}
demo

```

changing its size without effect on the ratio (larger)
```{r dpi=150}
# {r dpi=150}
demo

```

changing its width
```{r, fig.width = 14}
# {r, fig.width = 14}
demo
```

changing its height
```{r, fig.height = 14}
# {r, fig.height = 14}
demo
```

of course you can do them all together!!
```{r, fig.height = 5, fig.width = 5, fig.align="right"}
# {r, fig.height = 5, fig.width = 5, fig.align="right"}
demo
```


# 4. axis engineering
You can exchange the x and y axis
```{r, fig.height = 5, fig.width = 5, fig.align="center"}
demohist <- ggplot(df) +
  geom_histogram(aes(x = weight), bins = 10)

demohist+coord_flip()
```

You can reverse the y axis
```{r, fig.height = 5, fig.width = 5, fig.align="center"}
demohist+scale_y_reverse()
```

You can flip the histogram from right to left
```{r, fig.height = 5, fig.width = 5, fig.align="center"}
demohist+scale_y_reverse()+coord_flip()
```